Oregon 2013 Medication for Asthma Inhalers

### 2017-06-16 r_scripts/analysis/oregon_medication.Rmd
two state distributed lag??

```{r library, include=FALSE, echo=FALSE}
library(dplyr)
library(data.table)
library(readxl) 
library(readr)
library(survival)
library(ggplot2)
library(htmlTable)
library(knitr)
library(splines)
```

@@

```{r descriptive table, echo = F, message = F, warning = F, results='asis'}
read_path6 <- paste0("../data_new/medication/oregon_ndc_time_strat_casecrossover.csv")
asthma_ndc <- read_csv(read_path6)

@@

print(plot_ts)
# save figure
ggsave("../plot_new/ndc_ts.pdf", plot = plot_ts, 
       width = 12, height = 8, units = "in")
```

@@

@@

@@

```{r DLM, echo = FALSE, message=FALSE, warning=FALSE}

@@

asthma_ndc_lag <- asthma_ndc_df %>%
  filter(gender!="U") %>%
  filter(outcome==1) %>%
  select(88, 115:121) # GWR-method

@@

# true DL function
DLfunc <- exp(-(0:lag_max)/2)

# simulate outcomes
y <- drop(asthma_ndc_lag%*%DLfunc) # + rnorm(n)

@@

asthma_ndc_lag_B <- asthma_ndc_lag%*%B
fit <- lm(y~asthma_ndc_lag_B)
coef(fit)

dlparms <- grep("asthma_ndc_lag_B",names(coef(fit)))
DLestimate<- data.frame(estimate=B%*%coef(fit)[dlparms])
DLvar <- B%*%vcov(fit)[dlparms,dlparms]%*%t(B)
DLestimate$SE <- sqrt(diag(DLvar))
DLestimate$lower <- DLestimate$estimate + DLestimate$SE * qt(1-0.975, df=fit$df.residual)
DLestimate$upper <- DLestimate$estimate + DLestimate$SE * qt(0.975, df=fit$df.residual)
DLestimate

DLestimate$lag <- 0:lag_max
DLestimate$truth <- DLfunc
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag, y=truth), linetype=2, size=2)
p <- p + theme_bw()
p

cumulative <- sum(DLestimate$estimate)
cumulative
## [1] 2.485711
cumulative_se <- sqrt(sum(DLvar))
cumulative_se
## [1] 0.0001887442
cumulative_CI <- cumulative + cumulative_se * qt(c(1-0.975,0.975), df=fit$df.residual)
cumulative_CI
## [1] 2.485341 2.486080

@@

```{r overall lag1, warning =F, echo = F, results='asis'} 
# dataframe list

@@

@@

@@

@@

@@

>>>>

```{r library, include=FALSE, echo=FALSE}
library(tidyverse)
library(data.table)
library(readxl) 
library(readr)
library(survival)
library(ggplot2)
library(htmlTable)
library(knitr)

# two-stage distributed lag model libraries
library(dlnm)
library(mvmeta)
library(splines)

@@

```{r descriptive table, echo = F, message = F, warning = F, results='asis'}
read_path6 <- paste0("../data_new/medication/oregon_ndc_time_strat_casecrossover.csv")
asthma_ndc <- fread(read_path6, showProgress = T)

@@

print(plot_ts)

# save figure
ggsave("../plot_new/ndc_ts.pdf", plot = plot_ts, 
       width = 12, height = 8, units = "in")
```

@@

state_n_obs <- or_ndc_county_time_series %>% 
  select(county, date, n_obs) %>% 
  gather(key = n_obs, value = n, -date, -county)

count_plot <- ggplot(state_n_obs, aes(x = date, y = n)) +
  geom_point() +
  facet_wrap(~county+n_obs, scales = "free") +
  ylab("Outcome Counts") +
  xlab("Date") +
  theme_bw()

print(count_plot)

ggsave("../plot_new/ndc_county_ts2.pdf", plot = count_plot, 
       width = 12, height = 8, units = "in")

@@

### County
or_smk <- or_ndc_county_time_series_week %>% 
  select(county, date, wrf_smk_pm, krig_smk_pm, geo_smk_pm) %>% 
  gather(key = smk_method, value = pm, -date, -county)

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle("Oregon: 2013 Fire Season Smoke PM2.5") +
  ylab("Smoke PM2.5 ug/m^3") +
  xlab("Year: 2013") +
  theme_bw()

print(or_smk_plot)

ggsave("../plot_new/ndc_smoke_county.pdf", plot = plot_mult_week, 
       width = 12, height = 8, units = "in")

## Two stage distributed lag

```{r}
# create vector of state_county
counties <- as.character(unique(or_ndc_county_time_series$county))

# create dataframe list of each county
county_list_df <- lapply(counties, function(x) 
  or_ndc_county_time_series[or_ndc_county_time_series$county==x,])
# assign each element of the list object the county name
names(county_list_df) <- counties
# calculate length of counties (75)
m <- length(counties)

# GWR PM2.5 ranges
smk_range <- t(sapply(county_list_df, 
  function(x) range(x$geo_smk10,na.rm=T)))
# smk_range

# population range
pop_range <- t(sapply(county_list_df, 
  function(x) range(x$population,na.rm=T)))
# pop_range
# -----

# function to compute the QAIC (quasi-poisson AIC)
fqaic <- function(model) {
  loglik <- sum(dpois(model$y,model$fitted.values,log=TRUE))
  phi <- summary(model)$dispersion
  qaic <- -2*loglik + 2*summary(model)$df[3]*phi
  return(qaic)
}

# assuming linear relationship between smoke and outcomes
argvar <- list(fun="lin")

# fitting a natural spline of the lag function
degree_freedom <- 4
arglag <- list(fun="ns", df=degree_freedom)
# I'm not certain on lag yet, but maybe a week makes sense
lag <- 7

# overall cumulative summaries
# columns need to match degrees of freedom for lag
# 4 degrees of freedom for the spline
cumulative_counties <- matrix(NA, length(county_list_df), 
  as.numeric(degree_freedom), 
  dimnames=list(counties,paste("b",seq(degree_freedom),sep="")))

names(cumulative_counties) <- counties

# (co)variance matrices
counties_cov <- vector("list",length(county_list_df))
names(counties_cov) <- counties

# I also want to make a matrix of county-level models that fail to converge
converge <- matrix(NA, length(county_list_df), 1,
  dimnames=list(counties, "converge"))

# qaic
qaic_val <- 0

### first stage

```{r}
# first stage ----
# I'm not certain on time lag yet, but maybe a week makes sense
lag <- 7

# create outcome list to loop through
outcome_names <- "Asthma inhalers"
# copd is having issues; i suspect counties with no events is the problem
# empty vector to fill with error messages of counties where models can be run
# mostly due to no variation in the outcome (i.e. all 0s in the time series)

fit_matrix <- matrix(NA, nrow=0, ncol=6)
colnames(fit_matrix) <- c("outcome", "exposure", "fit_type", "df", "aic",
                           "n_mod_conv")

# 1st loop: loop through outcomes

# 2nd loop: vary degrees of freedom for lag knots
# set up empty matrix to assess model fit
fit_mat <- matrix(NA, nrow = 3, ncol = 6)

  # 2 df will not work for a spline, going from 3 to 6 df
  for(h in 3:5){ # start loop for df

    # fitting a natural spline for lag with 5 knots?
    fit_mat[h-2, 4] <- degree_freedom <- h
    arglag <- list(fun="ns", df=degree_freedom)

    # overall cumulative summaries
    # columns need to match degrees of freedom for lag
    # q: do i need to make this object multiple times or just fill it in?
    cumulative_counties <- matrix(NA, length(county_list_df), 
      as.numeric(degree_freedom), 
      dimnames=list(counties,paste("b",seq(degree_freedom),sep="")))

    names(cumulative_counties) <- counties

    # (co)variance matrices
    counties_cov <- vector("list",length(county_list_df))
    names(counties_cov) <- counties

    # I also want to make a matrix of county-level models that fail to converge
    converge <- matrix(NA, length(county_list_df), 1,
      dimnames=list(counties, "converge"))

    # empty table to log degrees of freedom and AIC for each outcome

    # qaic
    qaic_val <- 0

    # first stage ----
    # loop for each county
    for(i in seq(county_list_df)) {
      # if error in following code, move on to next county
      tryCatch({
      # load county-specific dataframe
      sub <- county_list_df[[i]]

      # run only if there is at least one observation of outcome in ts
      #if(max(sub[, which(colnames(sub)==outcome_names[[q]])]) > 2){

      # define the cross-basis ----
      suppressWarnings({
      # cross-basis for smoke
      smk_cb <- crossbasis(sub$geo_smk10,lag=lag,argvar=argvar,arglag=arglag)
      # cross-basis for temp
      temp_cb <- crossbasis(sub$wrf_temp, lag = lag, argvar = argvar,
                            arglag = arglag)
      })

      # run the first stage county-specific models
      county_model <- glm(as.formula(paste0(outcome_names[q], 
        "~ smk_cb + temp_cb + offset(log(population))")), 
        family = "quasipoisson", sub)

      # alert warning if there are convergence issues
      converge[i,] <- county_model$converged

      # reduction to summary results ---
      # prediction summary for smoke 10 ug/m^3 
      # uses cross reduce function
      suppressWarnings({
        cr_counties <- crossreduce(smk_cb, county_model, type = "var", value = 1)

        })

      # store results in matrix ---
      # daily lag results
      cumulative_counties[i,] <- coef(cr_counties)
      counties_cov[[i]] <- vcov(cr_counties)

      # Q-AIC
      qaic_val[i] <- fqaic(county_model)

        }, error = function(e){
          # print(names(county_list_df[i]))
          }
        ) # end try catch

      } # end loop for county estimates

    # error at hood river; using trycatch to keep going
    #which(counties[]=="OR_Hood River")

    # fill in the fit matrix ----
    fit_mat[,1] <- outcome_names[q]
    fit_mat[,2] <- exposure <- "wrf_smk10"
    fit_mat[,3] <- "ns"
    # subset qaic to only models that converged
    # sum the grand q aic and fill fit matrix
    fit_mat[h-2,5] <- round(sum(qaic_val[!is.na(converge)[]==T]),2)
    # fill in number of county models that successfully converge
    fit_mat[h-2, 6] <- length(which(converge==T))
    sum(complete.cases(qaic_val))

    } # end model fit loop

 fit_matrix <- rbind(fit_matrix, fit_mat)

# end outcome loop and system time

# now that we have a range of df/knots, I want to filter to the minimum aic
# for each outcome and print out that value in a table

lag_spline_best_fit <- as_tibble(fit_matrix) %>%  
  group_by(outcome) %>% 
  slice(which.min(aic))

# kable
knitr::kable(lag_spline_best_fit, caption = paste0("Distributed lag spline",
  "degree of freedom best fit by AIC for two-stage approach"))

```{r}
# set estimation method for multivariate approach
# reml estimation method
method <- "reml"

# create a dataframe that contains the distributed lag estimates for each outcome
dist_lag_df <- as_tibble(matrix(NA,  nrow = 0, ncol = 5))
colnames(dist_lag_df) <- c("outcome", "lag", "rel_risk", 
                                  "lower_95", "upper_95")

# produce results using fit matrix

# 1st loop: loop through outcomes
for(j in 1:length(lag_spline_best_fit$outcome)){

  j = 1
    # easiest to set out the parameters from the start
    outcome <- lag_spline_best_fit$outcome[j]
    degree_freedom <- as.numeric(lag_spline_best_fit$df[j])

    arglag <- list(fun="ns", df=degree_freedom)

    # overall cumulative summaries
    # columns need to match degrees of freedom for lag
    # q: do i need to make this object multiple times or just fill it in?
    cumulative_counties <- matrix(NA, length(county_list_df), 
      as.numeric(degree_freedom), 
      dimnames=list(counties,paste("b",seq(degree_freedom),sep="")))

    names(cumulative_counties) <- counties

    # (co)variance matrices
    counties_cov <- vector("list",length(county_list_df))
    names(counties_cov) <- counties

    # I also want to make a matrix of county-level models that fail to converge
    converge <- matrix(NA, length(county_list_df), 1,
      dimnames=list(counties, "converge"))

    # first stage loop for each county ----
    for(i in seq(county_list_df)) {
      # if error in following code, move on to next county using trycatch
      tryCatch({
      # load county-specific dataframe
      sub <- county_list_df[[i]]

      # define the cross-basis
      suppressWarnings({
      # cross-basis for smoke
      smk_cb <- crossbasis(sub$geo_smk10,lag=lag,argvar=argvar,arglag=arglag)
      # cross-basis for temp
      temp_cb <- crossbasis(sub$wrf_temp, lag = lag, argvar = argvar,
                            arglag = arglag)
      })

      # run the first stage county-specific models
      county_model <- glm(as.formula(paste0(outcome, 
        "~ smk_cb + temp_cb + offset(log(population))")), 
        family = "quasipoisson", sub)

      # alert warning if there are convergence issues
      converge[i,] <- county_model$converged

      # reduction to summary results ---
      # prediction summary for smoke 10 ug/m^3 
      # uses cross reduce function
      suppressWarnings({
        cr_counties <- crossreduce(smk_cb, county_model, type = "var", value = 1)
        })

      # store results in matrix ---
      # daily lag results
      cumulative_counties[i,] <- coef(cr_counties)
      counties_cov[[i]] <- vcov(cr_counties)
        }, error = function(e){
          #print(names(county_list_df[i]))
          }) # end try catch

      } # end loop for county estimates

  # second stage multivariate meta analysis ---- 
  # For counties with outcomes that will not even run, set their converge
  # from missing to False for subsetting
  converge[is.na(converge)] <- FALSE

  # first step is to reduce the county-specific matrix to those that converged
  meta_counties <- cumulative_counties[converge[]==T, ]
  # reduce covariance matrix to models that converged
  meta_cov <- counties_cov[converge[]==T]

  # overall pooled summary for asthma model
  cumulative_mv_meta <- mvmeta(meta_counties~1, meta_cov, method = method)

  # create bases for prediction ----
  # bases of smoke lag (7 days with 10 intervals in each)
  xlag <- 0:70/10
  blag <- do.call("onebasis",c(list(x=xlag),attr(smk_cb,"arglag")))

  # county-specific first stage summaries
  county_lag_estimates <- apply(cumulative_counties,1, function(x) exp(blag%*%x))

  # prediction for a grid of lag days
  # predictor-specific summaries for 10 ug/m^3 of smoke
  pooled_cp <- crosspred(blag, coef=coef(cumulative_mv_meta), 
    vcov=vcov(cumulative_mv_meta), model.link="log", at = xlag)

  # create empty dataframe to fill with estimates
  # fill lag relationship with outcome tibble
  # empty matrix to fill in distributed lag values
  outcome_smk_lag_df <- as_tibble(matrix(NA,  nrow = length(xlag), ncol = 5))
  # assign outcome name
  colnames(outcome_smk_lag_df) <- c("outcome", "lag", "rel_risk", 
                                  "lower_95", "upper_95")

  # fill dataframe with values
  outcome_smk_lag_df[,1] <- outcome
  outcome_smk_lag_df[,2] <- xlag
  outcome_smk_lag_df[,3] <- pooled_cp$matRRfit
  outcome_smk_lag_df[,4] <- pooled_cp$matRRlow
  outcome_smk_lag_df[,5] <- pooled_cp$matRRhigh

  # bind works better than trying to figure out how to fill many rows
  dist_lag_df <- rbind(dist_lag_df, outcome_smk_lag_df)

}

ggplot(dist_lag_df, aes(x=lag, y=rel_risk)) +
  geom_line(colour = "blue") +
  geom_ribbon(aes(ymin = lower_95, ymax = upper_95), fill = "blue", alpha = 0.3) + 
  scale_y_continuous(limits = c(0.9, 1.15)) +
  scale_x_continuous(breaks = c(seq(0, 7,by=1))) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  facet_wrap(~ outcome) +
  ggtitle(paste0("Distributed lag association between a 10 ug/m^3",
                 " increase in GWR smoke PM2.5 and cardiopulmonary outcomes")) +
  ylab("Relative Risk for a 10 ug/m^3 increase in GWR smoke (fixed)") +
  xlab("Lagged Days") +
  theme_bw()

@@

### Lag 1

```{r DLM, echo = FALSE, message=FALSE, warning=FALSE, eval=FALSE}
asthma_ndc_df <- data.frame(asthma_ndc)

asthma_ndc_df <- asthma_ndc_df %>% # GWR
  filter(!is.na(geo_wt_pm_lag7_zip)) # 503998

@@

asthma_ndc_lag <- asthma_ndc_df %>%
  select(88, 115:121) # GWR-method

@@

@@

asthma_ndc_lag_B <- asthma_ndc_lag%*%B
fit <- clogit(outcome ~ asthma_ndc_lag_B + wrf_temp_zip + strata(personkey), asthma_ndc_df)
coef(fit)
summary(fit)

dlparms <- grep("asthma_ndc_lag_B",names(coef(fit)))
DLestimate<- data.frame(estimate=B%*%coef(fit)[dlparms])
DLvar <- B%*%vcov(fit)[dlparms,dlparms]%*%t(B)
DLestimate$SE <- sqrt(diag(DLvar))
DLestimate$lower <- DLestimate$estimate - DLestimate$SE * 1.96
DLestimate$upper <- DLestimate$estimate + DLestimate$SE * 1.96

DLestimate$estimate <- exp(DLestimate$estimate)
DLestimate$lower <- exp(DLestimate$lower)
DLestimate$upper <- exp(DLestimate$upper)

DLestimate

DLestimate$lag <- 0:lag_max
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw()
p

DLestimate<- data.frame(estimate=B%*%coef(fit)[dlparms])

cumulative <- sum(DLestimate$estimate)
cumulative
## [1] 0.009141771
cumulative_se <- sqrt(sum(DLvar))
cumulative_se
## [1] 0.000955469
cumulative_CI <- cumulative + cumulative_se * c(-1.96, 1.96)
cumulative_CI
## [1] 0.007269052 0.011014490

@@

```{r overall lag 1, warning =F, echo = F, results='asis'} 
# dataframe list

@@

# outcome name
outcome <- "Asthma Inhalers Lag 1"
outcome_name <- "Asthma Inhalers Lag 1"

@@

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 three smoke method and pharmacy outcomes",
         # row group by outcome
         rgroup = "Asthma Inhalers Lag 1",
         n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Referent periods matched to events on same day of week within May to September fire season."
         ) # end table

@@

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

@@

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and health outcomes stratified by age",
         # row group by outcome
         rgroup = "Asthma inhalers Lag 1",
         n.rgroup = c(rep(9, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Age Group", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(4, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within May to September fire season."
         ) # end table

@@

  tab <- htmlTable(txtRound(wrf_geo_sex, digits = 3, 1:3), 
           caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and pharmacy outcomes stratified by sex",
           # row group by outcome
           rgroup = "Asthma inhalers Lag 1",
           n.rgroup = c(rep(6, 1)), # 2 rows for each sex strata for each outcome
           # column headers
           header = c("Est Method", "Sex Strata", "Events",
                      "OR&dagger;", "Lower", "Upper"),
           # column spanner
           cgroup = c("", "95% CI"), 
           n.cgroup = c(4, 2),
           padding.rgroup = "&nbsp;&nbsp;",
           css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
           align = "llcccc", # column alignment,
           tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within July to October fire season."
            ) # end table

### Lag 2

```{r overall lag 2, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "Asthma Inhalers Lag 1"
outcome_name <- "Asthma Inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 three smoke method and pharmacy outcomes",
         # row group by outcome
         rgroup = "Asthma Inhalers Lag 1",
         n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r time stratified age strata lag 2, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and health outcomes stratified by age",
         # row group by outcome
         rgroup = "Asthma inhalers Lag 1",
         n.rgroup = c(rep(9, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Age Group", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(4, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r sex strata cdc met  lag 2, warning = F, echo = F, results='asis'} 
method_list <- c('WRF-Chem Smoke', 'Kriging Smoke', 'Geo-Weighted Smoke')

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

  tab <- htmlTable(txtRound(wrf_geo_sex, digits = 3, 1:3), 
           caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and pharmacy outcomes stratified by sex",
           # row group by outcome
           rgroup = "Asthma inhalers Lag 1",
           n.rgroup = c(rep(6, 1)), # 2 rows for each sex strata for each outcome
           # column headers
           header = c("Est Method", "Sex Strata", "Events",
                      "OR&dagger;", "Lower", "Upper"),
           # column spanner
           cgroup = c("", "95% CI"), 
           n.cgroup = c(4, 2),
           padding.rgroup = "&nbsp;&nbsp;",
           css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
           align = "llcccc", # column alignment,
           tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within July to October fire season."
            ) # end table

### Lag 3

```{r overall lag 3, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "Asthma Inhalers Lag 1"
outcome_name <- "Asthma Inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 three smoke method and pharmacy outcomes",
         # row group by outcome
         rgroup = "Asthma Inhalers Lag 1",
         n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r time stratified age strata lag 3, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and health outcomes stratified by age",
         # row group by outcome
         rgroup = "Asthma inhalers Lag 1",
         n.rgroup = c(rep(9, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Age Group", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(4, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r sex strata cdc met  lag 3, warning = F, echo = F, results='asis'} 
method_list <- c('WRF-Chem Smoke', 'Kriging Smoke', 'Geo-Weighted Smoke')

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

  tab <- htmlTable(txtRound(wrf_geo_sex, digits = 3, 1:3), 
           caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and pharmacy outcomes stratified by sex",
           # row group by outcome
           rgroup = "Asthma inhalers Lag 1",
           n.rgroup = c(rep(6, 1)), # 2 rows for each sex strata for each outcome
           # column headers
           header = c("Est Method", "Sex Strata", "Events",
                      "OR&dagger;", "Lower", "Upper"),
           # column spanner
           cgroup = c("", "95% CI"), 
           n.cgroup = c(4, 2),
           padding.rgroup = "&nbsp;&nbsp;",
           css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
           align = "llcccc", # column alignment,
           tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within July to October fire season."
            ) # end table

### Lag 4

```{r overall lag 4, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "Asthma Inhalers Lag 1"
outcome_name <- "Asthma Inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 three smoke method and pharmacy outcomes",
         # row group by outcome
         rgroup = "Asthma Inhalers Lag 1",
         n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r time stratified age strata lag 4, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and health outcomes stratified by age",
         # row group by outcome
         rgroup = "Asthma inhalers Lag 1",
         n.rgroup = c(rep(9, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Age Group", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(4, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r sex strata cdc met  lag 4, warning = F, echo = F, results='asis'} 
method_list <- c('WRF-Chem Smoke', 'Kriging Smoke', 'Geo-Weighted Smoke')

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

  tab <- htmlTable(txtRound(wrf_geo_sex, digits = 3, 1:3), 
           caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and pharmacy outcomes stratified by sex",
           # row group by outcome
           rgroup = "Asthma inhalers Lag 1",
           n.rgroup = c(rep(6, 1)), # 2 rows for each sex strata for each outcome
           # column headers
           header = c("Est Method", "Sex Strata", "Events",
                      "OR&dagger;", "Lower", "Upper"),
           # column spanner
           cgroup = c("", "95% CI"), 
           n.cgroup = c(4, 2),
           padding.rgroup = "&nbsp;&nbsp;",
           css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
           align = "llcccc", # column alignment,
           tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within July to October fire season."
            ) # end table

### Lag 5

```{r overall lag 5, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "Asthma Inhalers Lag 1"
outcome_name <- "Asthma Inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 three smoke method and pharmacy outcomes",
         # row group by outcome
         rgroup = "Asthma Inhalers Lag 1",
         n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r time stratified age strata lag 5, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and health outcomes stratified by age",
         # row group by outcome
         rgroup = "Asthma inhalers Lag 1",
         n.rgroup = c(rep(9, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Age Group", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(4, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r sex strata cdc met  lag 5, warning = F, echo = F, results='asis'} 
method_list <- c('WRF-Chem Smoke', 'Kriging Smoke', 'Geo-Weighted Smoke')

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"

  tab <- htmlTable(txtRound(wrf_geo_sex, digits = 3, 1:3), 
           caption = "Association between a 10 ug/m^3 in PM2.5 geo smoke and pharmacy outcomes stratified by sex",
           # row group by outcome
           rgroup = "Asthma inhalers Lag 1",
           n.rgroup = c(rep(6, 1)), # 2 rows for each sex strata for each outcome
           # column headers
           header = c("Est Method", "Sex Strata", "Events",
                      "OR&dagger;", "Lower", "Upper"),
           # column spanner
           cgroup = c("", "95% CI"), 
           n.cgroup = c(4, 2),
           padding.rgroup = "&nbsp;&nbsp;",
           css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
           align = "llcccc", # column alignment,
           tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within July to October fire season."
            ) # end table

### Lag 6

```{r overall lag 6, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "Asthma Inhalers Lag 1"
outcome_name <- "Asthma Inhalers Lag 1"

tab <- htmlTable(txtRound(wrf_geo_age, digits = 3, 1:3), 
         caption = "Association between a 10 ug/m^3 in PM2.5 three smoke method and pharmacy outcomes",
         # row group by outcome
         rgroup = "Asthma Inhalers Lag 1",
         n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Est Method", "Events",
                    "OR&dagger;", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Referent periods matched to events on same day of week within May to September fire season."
         ) # end table

```{r time stratified age strata lag 6, warning =F, echo = F, results='asis'} 
# dataframe list

# outcome name
outcome <- "asthma inhalers Lag 1"
outcome_name <- "Asthma inhalers Lag 1"
